Indexes measures for oak decline severity using phenotypic descriptors

### 2019-08-27 manuscript/manuscript.Rmd
added equations

---
title: "Indexes measures for oak decline severity using phenotypic descriptors"
output: pdf_document
---

@@

```{r figure_1}
source('../code/Figure_1_site_differences.R')

figure1 %>%
  wrap_plots()
```

>>>>

---
title: "Indexes measures for oak decline severity using phenotypic descriptors"
output: pdf_document
keep_tex: yes
---

@@

# Introduction

# Materials and methods

# Results

## Additional Descriptors

**Crown condition (%)** - percentage of present crown proportional to the percentage crown density.

$$c = (100 - m)(1-\frac{t}{100})$$

$m$ = missing crown (%), $t$ = crown transparency (%)

**Estimated crown volume (m<sup>3</sup>)** - estimated volume of crown as an ellipsoid proportional to the crown condition.

$$v = \frac{c(h - l)}{150}\pi r^2$$

$r$ = crown radius (m), $h$ = total height (m), $l$ = lower crown height (m), $c$ = crown condition (%)

**Estimated bleed prevalence (%)** - estimated percentage of the surveyed trunk area affected by bleeds or black staining.

$$p = \frac{a^2A + b^2B}{3d\pi}$$

$a$ = average active bleed size (cm), $A$ = number of active bleeds, $b$ = average black stain size (cm), $B$ = black stain number, $d$ = diameter at breast height (cm)

***Agrilus* exit hole density (m<sup>-2</sup>)** - density of observed *Agrilus* exit holes across the surveyed trunk area.
$$e = \frac{h}{\frac{2d}{100}\pi}$$
$h$ = number of *Agrilus* exit holes, $d$ = diameter at breast height (cm)
```{r site_differences}
source('../code/site_differences.R')
site_differences %>%
  wrap_plots()
```
```{r descriptor_adjustment,fig.cap='Error bars show ±1SE of the mean.\nDashed red line shows the overall mean.'}
source('../code/descriptor_adjustment.R')
descriptor_adjustment %>%
  wrap_plots()
```
```{r DIspace}
DIspace()
```
```{r}
source('../code/descriptor_contributions.R')
descriptor_contributions %>%
  wrap_plots() + 
  plot_annotation(title = 'Descriptor importance scores from random forest models for relative contributions to\ndecline index measures',caption = 'Gini importance scores averaged across 100 repetitions')
```
# Discussion
# Conclusions
# References
